PANCHANGE_analysis

### 2021-03-08 PANCHANGE_analysis.Rmd
added by sample retro regression for PHQ and PCL

## GLAD
```{r gad employment prior covid sensitivity model1b sum_score retro by sample glad}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro.glad")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

## NBR
```{r gad employment prior covid sensitivity model1b sum_score retro by sample nbr}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro.nbr")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

## RAMP
```{r gad employment prior covid sensitivity model1b sum_score retro by sample ramp}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro.ramp")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

>>>>

## GAD

### GLAD
```{r gad employment prior covid sensitivity model1b sum_score retro by sample glad}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro.glad")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

### NBR
```{r gad employment prior covid sensitivity model1b sum_score retro by sample nbr}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro.nbr")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

### RAMP
```{r gad employment prior covid sensitivity model1b sum_score retro by sample ramp}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro.ramp")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

## PHQ

### GLAD
```{r phq employment prior covid sensitivity model1b sum_score retro by sample glad}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro.glad")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

### NBR
```{r phq employment prior covid sensitivity model1b sum_score retro by sample nbr}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro.nbr")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

### RAMP
```{r phq employment prior covid sensitivity model1b sum_score retro by sample ramp}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro.ramp")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

## PCL

### GLAD
```{r pcl employment prior covid sensitivity model1b sum_score retro by sample glad}
# Regression coefficients
pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                                                               explan_var = "pcl.sum_score_retro",
                                                               data_set = "dat.retro.glad")
kable(pcl_retro_model1b_explan_estimates)
pcl_retro_model1b_explan_estimates

### NBR
```{r pcl employment prior covid sensitivity model1b sum_score retro by sample nbr}
# Regression coefficients
pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                                                               explan_var = "pcl.sum_score_retro",
                                                               data_set = "dat.retro.nbr")
kable(pcl_retro_model1b_explan_estimates)
pcl_retro_model1b_explan_estimates

### RAMP
```{r pcl employment prior covid sensitivity model1b sum_score retro by sample ramp}
# Regression coefficients
pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                                                               explan_var = "pcl.sum_score_retro",
                                                               data_set = "dat.retro.ramp")
kable(pcl_retro_model1b_explan_estimates)
pcl_retro_model1b_explan_estimates
